Proposed Solution

### 2017-01-25 CAV17/secs/concl.tex
cav17: stuff

In this paper, we introduce \app, a highly modular framework 
that allows automatic verification of configuration files.
\app employs a translator to parse a training set
of configuration files into an intermediate representation,
and then uses a learner module to derive rules.
\app finally uses post analysis module to refine these learned
rules, enabling users to verify the configuration files of
their interest.
Our evaluation based on a real-world misconfiguration
dataset~\cite{configdataset} shows that \app is able to
correctly detect configuration errors
including ordering, missing entry, integer correlation
and type errors.

>>>>

In this paper, we introduce \app, a highly modular framework 
that allows automatic verification of configuration files.
\app employs a translator to parse a training set
of configuration files into an intermediate representation,
and then uses a learner module that employs
the association rule learning algorithm to derive rules.
\app finally uses rule graph analysis module to refine these learned
rules, enabling users to verify the configuration files of
their interest.
Our evaluation based on a real-world misconfiguration
dataset~\cite{configdataset} shows that \app is able to
correctly detect configuration errors
including ordering, missing entry, integer correlation
and type errors.

### 2017-01-25 CAV17/secs/eval.tex
cav17: stuff

We record the histogram of errors across the test set in Fig.~\ref{fig:histo}.
This is intuitively an expected result from randomly sampling Github - most repositories will have few errors, with an increasingly small number of repositories having many errors.

@@

The errors reported may have varying impacts on the system, ranging from failing to start, runtime crash, or performance degradation.
However, since \app is a probabilistic system, it is also possible that some errors are false positives, a violation of the rule has no effect on the system.
Note that in contrast to program verification, we do not have an oracle for determining if a reported error is a true error or a false positive.
While we can run a program to determine the effect a specification has on the success of compiling/running the program, no such test exists for configuration files.
Because configurations are dependent on the rest of the system (\ie the available hardware, the network speed, and the usage patterns), we cannot simulate the all conditions to determine if a reported error will cause system failure.
As evidenced by Example~\ref{ex:fine}, some misconfigurations will only cause greater than expected performance degradation, and only under particular traffic loads.
In light of this, the definition of a true error is necessarily imprecise.

>>>>

We record the histogram of errors across the test set in Figure~\ref{fig:histo}.
This is intuitively an expected result from randomly sampling Github - most repositories will have few errors, with an increasingly small number of repositories having many errors.

@@

The errors reported may have varying impacts on the system, ranging from failing to start, runtime crash, or performance degradation.
However, since \app is a probabilistic system, it is also possible that some errors are false positives, a violation of the rule has no effect on the system.
Note that in contrast to program verification, we do not have an oracle for determining if a reported error is a true error or a false positive.
While we can run a program to determine the effect a specification has on the success of compiling/running the program, no such test exists for configuration files.
Because configurations are dependent on the rest of the system (\ie, the available hardware, the network speed, and the usage patterns), we cannot simulate the all conditions to determine if a reported error will cause system failure.
As evidenced by Example~\ref{ex:fine}, some misconfigurations will only cause greater than expected performance degradation, and only under particular traffic loads.
In light of this, the definition of a true error is necessarily imprecise.
